Design Document for Relevance-Weighting: R Package glmm

### 2019-07-18 DesignDocs/DesignDocWeights.tex

>>>>

\section{Summary Changes}

The coefficient estimates in the summary should be changed in order to reflect the certainty known from the Monte Carlos standard error (\texttt{mcse}). This means that \texttt{glmm} must:

\begin{enumerate}
\item Detect the position of the first non-zero digit in the \texttt{mcse} estimates;
\item Round the coefficient estimates in the \texttt{glmm} summary to the number of digits detected in step 1.
\end{enumerate}
